# STA 141 Assignment 1

# #1 what are the dimensions of the dataset?
```{r}

load("C:/Users/Der-chan/Downloads/vehicles.rda")
dim(vposts)

```


# #2 What are the names of the variables? and what is the class of each variable

```{r}
sapply(vposts, class)
names(vposts)
```

# #3 What is the average price of all the vehicles? the median price? and the deciles? Displays these on a plot of the distribution of vehicle prices.
```{r}
#price mean
mean(vposts$price, na.rm = TRUE)
#price median
median(vposts$price, na.rm = TRUE)
#deciles for vehicle prices
quantile(vposts$price, c(0, .1, .2, .3, .4, .5, .6, .7, .8, .9 ,1), na.rm = TRUE)


## re-did these to account for $1 listings. Sometimes sellers list items at this price to have them show up first on "lowest to highest" price setting

mean(vposts$price[which(vposts$price > 100)], na.rm =TRUE)
median(vposts$price[which(vposts$price > 100)], na.rm = TRUE)
quantile(vposts$price[which(vposts$price > 100)], c(0, .1, .2, .3, .4, .5, .6, .7, .8, .9 ,1), na.rm = TRUE)
```

# #4 What are the different categories of vehicles, i.e. the type variable/column? What is the proportion for each category ?
```{r}
levels(vposts$type)
print(summary(vposts$type[!is.na(vposts$type)])/length(vposts$type[!is.na(vposts$type)]), digits = 3)

##note: I did this first with NA values, but they accounted for 45%, so I removed them
```

# #6 How many different cities are represented in the dataset?

```{r}
length(levels(vposts$city))
```

# #7 Visually display how the number/proportion of "for sale by owner" and "for sale by dealer" varies across city?
```{r}
mosaicplot(vposts$city~vposts$byOwner, 
           main = "Mosaic Plot of Seller vs. City",
           xlab = "City", ylab = "For Sale By Owner",
           color = TRUE)
##comes out at nearly 50% for each
```
# #8 What is the largest price for a vehicle in this data set? Examine this and fix the value. Now examine the new highest value for price.
```{r}
max(vposts$price, na.rm = TRUE)
max(vposts$price[which(vposts$price < 600030000)])

quantile(vposts$price[which(vposts$price > 100 & vposts$price < 600030000)], c(0, .1, .2, .3, .4, .5, .6, .7, .8, .9999 ,1), na.rm = TRUE)
```




#11 Plot the locations of the posts on a map? What do you notice?
```{r}
library(maps)
map('state')
map('state', c("Massachusetts", "Illinois","Colorado", "Nevada", "New York","California"), add = TRUE, fill = TRUE, col = "red")
points(vposts$long, vposts$lat, col = "blue", pch = ".")
##High density of cars for sale in metropolitan areas
```








